### 2024-08-14 manuscript.tex
Voyage references and small edits

Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December;
MCQ16-18 (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
February, 21 March 2017; TAN1502 (1 day): 24 January.

@@

ERA5 \citep{era5} is a reanalysis produced by the European Centre for
Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
horizontal resolution is 0.25° in latitude and longitude, which is about
28 km in the North--South direction and 14 km in the East--West direction at
60°S. The model uses 137 vertical levels. In our analysis we use output
at one hourly instantaeous time intervals, except for radiation quantities,
which are accumulations (from these we calculate daily means).
Vertically-resolved quantities are specified on pressure levels. We interpolate
these quantities to height levels as needed.

@@

\begin{table}
% TODO: Add sampling intervals.
\caption{List of voyages and stations. Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40°S. Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate CL31.}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
Name & Vessel & Ceil. & Region & Start & End & Days\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124\\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149\\
MCQ16-18 & /                             & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710\\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

\begin{figure}
\centerline{
\includegraphics[width=1.06\textwidth]{img/cloud_occurrence_panel.pdf}
}
\caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
station (MCQ16-18) in observations (OBS), and simulated by the ALCF from the
ICON model, MERRA‐2 (M2) and ERA5 reanalysis data. The numbers in the legend
indicate the total cloud fraction and the number of days of data.}
\label{fig:cloud-occurrence-panel}
\end{figure}

>>>>

Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December;
MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
February, 21 March 2017; TAN1502 (1 day): 24 January.

@@

ERA5 \citep{era5} is a reanalysis produced by the European Centre for
Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
horizontal resolution is 0.25° in latitude and longitude, which is about
28 km in the North--South direction and 14 km in the East--West direction at
60°S. Internally, the model uses 137 vertical levels. In our analysis we use
output at one hourly instantaeous time intervals, except for radiation
quantities, which are accumulations (from these we calculate daily means).
Vertically-resolved quantities are made available on 37 pressure levels. We
interpolate these quantities to height levels as needed.

@@

\begin{table}
% TODO: Add sampling intervals.
\caption{List of voyages and stations. Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40°S. Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate CL31.}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
Name & Vessel & Ceil. & Region & Start & End & Days\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
MICRE    & [Macquarie Is. station]       & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

\begin{table}
\caption{List of voyages and station references.}
\label{tab:voyage-references}
\small
\begin{tabular}{ll}
Name & References\\
\hline
AA15-16  & \cite{klekociuk2020} \\
MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019} \\
MICRE    & \cite{marchand2015,marchand2020} \\
PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
TAN1802  & \cite{kremser2021} \\
\end{tabular}
\end{table}

\begin{figure}
\centerline{
\includegraphics[width=1.06\textwidth]{img/cloud_occurrence_panel.pdf}
}
\caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
station (MICRE) in observations (OBS), and simulated by the ALCF from the
ICON model, MERRA‐2 (M2) and ERA5 reanalysis data. The numbers in the legend
indicate the total cloud fraction and the number of days of data.}
\label{fig:cloud-occurrence-panel}
\end{figure}
